### 2014-08-21 SP_simul.Rmd
Add local multifractal approach to introduction

spa <- genBand_image(64,256)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_256.sed")

@@

spa <- genBand_image(64,512)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_512.sed")

@@

require(untb)
side <- 512
N <- side*side
S <- 64 
repeat {
  ff<-fisher.ecosystem(N=N,S=S,nmax=N)
  nsp <- nrow(ff)
  if(nsp==S) break
}
plot(ff)
N
spa <- matrix(rep(1:nsp,ff),nrow=side)
plot_sed_image(spa,"Regular Fisher  64sp")
save_matrix_as_sed(spa,"fish64_512.sed")

>>>>

spa <- genUniformSAD_image(64,256)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_256.sed")

@@

spa <- genUniformSAD_image(64,512)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_512.sed")

@@

# Generate an image following a logseries distribution with 64 sp 
# an regular spatial distribution
spa <- genFisherSAD_image(64,512)

plot_sed_image(spa,"Regular Fisher  64sp",0,64,10)
save_matrix_as_sed(spa,"fish64_512.sed")
